CSD, Disjoint components and trayectory detection

### 2019-11-15 ArticuloCSDyCM/Paper03.tex
mas trazos evocado

\documentclass[12pt, letterpaper]{article}

@@

\usepackage{setspace}
\usepackage{lineno} %ambos paquetes para borrador

@@

@@

@@

Center of Mass Analysis (CMA) has been used previously in order to track putative  ``trajectories'' of the activity or information across neural tissue or even the whole brain \cite{Chao05, Chao07, Manjarrez07, Manjarrez09}. In such works the chosen ``mass'' was an heuristic measure adequate for representing the coarse-grain picture of displacement of activity. These present the problem of justifying the choice made on practical grounds. For calculating a vectorial average, the adequate weight per vector is a density, a positive quantity that measures the concentration of something per space unit, so it is only adequate that we search for a natural density in the electrophysiological experiments. The Current Source Density fits the mathematical and interpretative requirements. We shall denote it in the following as $C$ (following \cite{Potworowski2011}).  This measure is usually presented in arbitrary units, which permits us to interpret it two-fold. One, directly from its definition, as the \emph{differential divergence} of the vectorial electric current density:
\begin{equation}
  C:=\nabla \cdot J
\end{equation}
Due to conservation of charges, this is the same as as the temporal variation of density of charge:
\begin{equation}
  C=-\frac{\partial \rho}{\partial t}
\end{equation}
Current Source Density as a mathematical density (a quasi-probability density function)  allows  to rigorously apply the concepts of vector averaging. This use has been overlooked. This might have occurred because  samplings at lesser spatial resolution did not permit estimations of this quantity with enough precision to make reliable spatial implications, even with the use of sophisticated CSD estimation methods. In our case, we want to use the density as a mathematician would: a function which assigns weights to points in the space of interest and permits us to carry linear operations over them.  The space here is the sampling points of the electrodes at a given instant in time, and the weight, the CSD, is amount of interchange of charged ions from the inside to the outside of cellular membranes, per unit space.  This is an indicator of activity in the neurons, therefore the CSD is also, indirectly, a \emph{``density of local activity''}. Having both
the mathematician and electrophysiologist interpretations presents we can
perform the following analysis with clear readings.

@@

\begin{figure}
  \includegraphics[width=0.9\textwidth]{Figuras/ExplicaDisconexos01.pdf}
  \caption{ Explanation of the geometrical concepts used on our analysis.
    In the Row A of figures
    with an artificial example the concepts of connectedness and convexity.
    The subfigure Ai shows
    three sets, $A$, $B$, and $C$. $A$ fails to be convex because it is concave,
    and $C$ fails to be
    be convex because it is made of two disconnected components.
    In each of them is possible to draw a line
    connecting two points inside the set that is not entirely inside the set.
    In $B$ that is not possible, the set $B$ is convex in a mathematical sense.
    In subfigure Aii we made some modification to show that
    each set can be made of many disconnected components,
    and each one of them can be convex or not.  In Aiii we show the center of
    mass for $A$ and $B$
    taken as a whole, while for $C$ we break the set into each of the disconnected
    components and calculate each CM separately. There is no guarantee that each
    disconnected component would be convex, but as the resolution of the data is finite,
    small components are more likely to
    be convex. In figure B we show everything with a frame of experimental data.
    In Bi we sepparate the
    data into three sets, Sources, Sinks, and Zeros.
    We discard the Zeros and keep the active ones.
    In Figure Bii we take the Sink Set and separate it into disconnected components,
    they are labeled from one to 25 in this particular example,
    indicated by color
    For each subset we sum over its mass, and 
    considerate for the next step those who are above certain threshold. The
    next step is shown in Biii, where we plot the Center of Mass for each of
    such subsets. Deviations
    from convexity are tolerable,
    as most of the mass is concentrated in the inner electrodes
    of each set.
  }
  \label{disconnectedsets}
\end{figure}

@@

The necessity to create such analysis came originally from the study of
electro-physiological data obtained from the rat's hippocampus, using
a very dense MEA, the BioCAM of 3Brain \cite{BioCAM}. 
The highly layered CA structure of the hippocampus provides strong, discernible patterns of Sources and Sinks. Following the paths of activity using Center of Mass analysis directly from the data, though, proves unfruitful, due to the non-convex nature of the somatic layer. Using CSD and disconnected component tracking over the data provided the right conceptual framework to follow the displacement of active areas during highly active events, such as epileptic-like activity that was pharmacological
or traumatically induced. The proposed analysis would not produce vector averages over different simultaneously active areas. On the contrary, it would separate them and track them independently. So the most violent epileptic burst provided us with the data necessary to prove the robustness of the method.
All the experimental data comes from a series of experiments
performed on slices of the rats hippocampus.

@@

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{Figuras/lfpevocado01.pdf}
  \caption{A set of frames showing the stimulus and posterior activity.
    The frame titled ``0 ms'' is just before the stimulus was
    made.  A diagram of the Granular and Pyramidal Layers is shown
    against the noice background. The black rectangle delimites the
    r.o.i. and the black arrow shows the site of stimulation in GD.
  }\label{lfpevocada}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_completa_evocada3R7.pdf}
\caption{ Comparison of the activity represented as LFP, CSD and CM.
  The time after
  stimulation in ms is shown in the central column for each row.
  In this series of frames a relatively big patch of the electrodes
  still appear saturated, but even so the CSD shows good localization
  of the relevant deflections from the neutral or noise base signal.
  The CM representation concentrates the locus of action even more.
  The circular dots in the third column represent the center of mass
  of coherent active subsets.
}\label{lfpcsdcm}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_sub_evocada3R7.pdf}
\caption{ The same as previous figure, but focusing on the
  region of interest, including the stratum pyramidale of CA3. A different
  color scheme was choosen on the last column, so as to provide borders
  that show how the disconnected componentes where choosen. 
}\label{lfpcsdcmsub}
\end{figure}

@@

\begin{figure}[H]
 \includegraphics[width=0.7\textwidth]{./Figuras/trayevocadasub.pdf}
  \caption{The evoked trajectories in the r.o.i. We begin to track them
    at the 0.9 ms mark, after letting the saturation of the stimulus recede.
    At 3ms a very clear sink trajectory is moving retrogradly towards CA2,
    sheepherd by two shorter source trayectories. At 5.6 a depolarization
    trajectory starts, following almost the same path and presenting also its
    two companions, ending around the 7.7ms timestamp. No significant
  trajectories are observed after the 10ms mark. }\label{evotracks}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=0.7\textwidth]{Figuras/diagfacilitada.pdf}
  \caption{A diagram of the approximate location of the pyramidal and granular strata on the hippocampus slice, during a peak of activity as measured in \muV{}.
  }
  \label{diagfaci}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_facilitada.pdf}
\caption{ Comparison of the activity represented as LFP, CSD and CM,
  in the same style as fig. \ref{lfpcsdcm}, but for facilitated activity.
  In this case the time counter starts at some moment around 80 ms. before the
  onset of the burst of activity.
}\label{lfpcsdcmfaci}
\end{figure}

\begin{figure}[H]
 \includegraphics[width=0.7\textwidth]{./Figuras/trayfaciljuntas.pdf}
 \caption{The trajectories for  the facilitated activity, in
 sequence of aparition around the burst of action.}\label{facitracks}
\end{figure}

\begin{figure}[H]
 \includegraphics[width=0.7\textwidth]{./Figuras/traytodasfacilitada.png}
 \caption{The trajectories for  the facilitated activity, shown
 all together.}\label{facitracktodas}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{./Figuras/LFPvsCSD_4AP.pdf}
  \caption{Comparison of LFP and CSD representations
    at the moments of the epileptic burst. In the first row
    we present the data as measured, no denoising or filtering has
    been applied. The units of measurement are in $\muV{}$. In
    the middle row a direct application of a difference operator
    gives us the CSD. This sort of operators are very sensitive
    to noise, in this case, spatial hard edges, which become
    greatly exaggerated. In the third row we present the same
    data after a Gaussian spatial filter ( Gaussian Blur) has
    been applied. }\label{lfpycsd4ap}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{./Figuras/Fronteras2sigma.pdf}
  \caption{The detection of disconnected components for the Sink and Source
    Sets. We take the the threshold value as two times the
    standard deviation of the whole data in CSD representation. In
    the upper row the data without the Gaussian Blur filtering is shown.
    Although the location of some of the active sets is clear, a lot of the
    joint activity gets hidden under the spatial noise. In the lower
    row we repeat the detection with the smoothed data. Large, coherent
    patches of activity are clearly shown, and the structure of the
    stratum pyramidale is apparent. 
  }\label{csdfrontera}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{./Figuras/SeqTray4AP01.pdf}
  \caption{ The activity in the Center of Mass and Trajectories representation.
    A single epileptic attack is shown from slightly before the onset until the
    last wave of the attack. Sink and Source trajectories are shown in blue
    and red, respectively. In order to not saturate the latter subfigures
    we take a persistence value of 2 ms, meaning that we do not shown
    trajectories 2 ms after they have ended.}\label{tray4ap}.
 \end{figure}

@@

The stratial tissue is an example of where this analysis cannot be used.
The limitations of this analysis are that it works  in
ordered, stratified neuronal tissue, and highly homogeneous tissue
without clear structures makes the distintion of both the CSD
disconnected sets unfeasible.

>>>>

\documentclass[11pt, letterpaper]{article}

@@

\usepackage{setspace}
\usepackage{lineno} %ambos paquetes para borrado

@@

\usepackage{caption}

@@

\newenvironment{intension}{\fontfamily{phv}\selectfont}{\par}

@@

Center of Mass Analysis (CMA) has been used previously in order to track putative  ``trajectories'' of the activity or information across neural tissue or even the whole brain \cite{Chao05, Chao07, Manjarrez07, Manjarrez09}. In such works the chosen ``mass'' was an heuristic measure adequate for representing the coarse-grain picture of displacement of activity. These present the problem of justifying the choice made on practical grounds. For calculating a vectorial average, the adequate weight per vector is a density, a positive quantity that measures the concentration of something per space unit, so it is only adequate that we search for a natural density in the electro-physiological experiments. The Current Source Density fits the mathematical and interpretative requirements. We shall denote it in the following as $C$ (following \cite{Potworowski2011}).  This measure is usually presented in arbitrary units, which permits us to interpret it two-fold. One, directly from its definition, as the \emph{differential divergence} of the vectorial electric current density:
\begin{equation}
  C:=\nabla \cdot J
\end{equation}
Due to conservation of charges, this is the same as as the temporal variation of density of charge:
\begin{equation}
  C=-\frac{\partial \rho}{\partial t}
\end{equation}
Current Source Density as a mathematical density (a quasi-probability density function)  allows  to rigorously apply the concepts of vector averaging. This use has been overlooked. This might have occurred because  samplings at lesser spatial resolution did not permit estimations of this quantity with enough precision to make reliable spatial implications, even with the use of sophisticated CSD estimation methods. In our case, we want to use the density as a mathematician would: a function which assigns weights to points in the space of interest and permits us to carry linear operations over them.  The space here is the sampling points of the electrodes at a given instant in time, and the weight, the CSD, is amount of interchange of charged ions from the inside to the outside of cellular membranes, per unit space.  This is an indicator of activity in the neurons, therefore the CSD is also, indirectly, a \emph{``density of local activity''}. Having both
the mathematician and electro-physiologist interpretations presents we can
perform the following analysis with clear readings.

@@

\begin{figure}[H]
  \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.9\textwidth]{Figuras/explicadisconected.pdf}
  \caption[tu abuela]{
   %& \begingroup
    %  \fontfamily{ppl}\selectfont
    \begin{intension}
      El propósito de esta figura es aclarar los conceptos usados
      para obtener los centros de masa en componentes disconexos.
      En la parte A
      se detalla con ejemplos artificiales los conceptos de
      convexo, disjunto y disconexo, y se muestran sus
      efectos sobre el cálculo de centros de masa. En la parte B
      se encuentra una aplicación a un recuadro de datos experimentales
      para que quede claro como se ven los pasos del análisis
      en un caso real.
      La primera parte indica a grosso modo la localización
      del str. pyr. y como en un cuadro específico
      se separan los datos en los conjuntos disjuntos de Pozos y Fuentes.
      En las partes ii y iii se muestra como se separan los componentes
      disconexos y se obtienen para cada uno su centro de masa.
      \end{intension}
   %   \endgroup

    Explanation of the geometrical concepts used on our analysis.
    In the Row A of figures
    with an artificial example the concepts of connectedness and convexity.
    The subfigure Ai shows
    three sets, $A$, $B$, and $C$. $A$ fails to be convex because it is concave,
    and $C$ fails to be
    be convex because it is made of two disconnected components.
    In each of them is possible to draw a line
    connecting two points inside the set that is not entirely inside the set.
    In $B$ that is not possible, the set $B$ is convex in a mathematical sense.
    In subfigure Aii we made some modification to show that
    each set can be made of many disconnected components,
    and each one of them can be convex or not.  In Aiii we show the center of
    mass for $A$ and $B$
    taken as a whole, while for $C$ we break the set into each of the disconnected
    components and calculate each CM separately. There is no guarantee that each
    disconnected component would be convex, but as the resolution of the data is finite,
    small components are more likely to
    be convex. In figure B we show everything with a frame of experimental data.
    In Bi we separate the
    data into three sets, Sources, Sinks, and Zeros.
    We discard the Zeros and keep the active ones.
    In Figure Bii we take the Sink Set and separate it into disconnected components,
    they are labeled from one to 25 in this particular example,
    indicated by color
    For each subset we sum over its mass, and 
    considerate for the next step those who are above certain threshold. The
    next step is shown in Biii, where we plot the Center of Mass for each of
    such subsets. Deviations
    from convexity are tolerable,
    as most of the mass is concentrated in the inner electrodes
    of each set.
  }
  \label{disconnectedsets}
\end{figure}

@@

The necessity to create such analysis came originally from the study of
electro-physiological data obtained from the rat's hippocampus, using
a very dense MEA, the BioCAM of 3Brain \cite{BioCam}. 
The highly layered CA structure of the hippocampus provides strong, discernible patterns of Sources and Sinks. Following the paths of activity using Center of Mass analysis directly from the data, though, proves unfruitful, due to the non-convex nature of the somatic layer. Using CSD and disconnected component tracking over the data provided the right conceptual framework to follow the displacement of active areas during highly active events, such as epileptic-like activity that was pharmacological
or traumatically induced. The proposed analysis would not produce vector averages over different simultaneously active areas. On the contrary, it would separate them and track them independently. So the most violent epileptic burst provided us with the data necessary to prove the robustness of the method.
All the experimental data comes from a series of experiments
performed on slices of the rats hippocampus.

@@

\begin{figure}[H]
  \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.9\textwidth]{Figuras/lfpevocado01.pdf}
  \caption[tu abuela]{
    \begin{intension}
      Aquí mostramos como se ve el registro crudo del potencial
      en un evento evocado. Tenmos los primeros recuadros super
      saturados, y a partir del milisegundo 4 podemos
      empezar a discernir las estructuras. Los electrodos
      más cercanos al sitio de estimulación quedan inutilizados.
      Es un ejemplo de las medidas en crudo en un caso dificil de usar.
     \end{intension}

    A set of frames showing the stimulus and posterior activity.
    The frame titled ``0 ms'' is just before the stimulus was
    made.  A diagram of the Granular and Pyramidal Layers is shown
    against the noise background. The black rectangle delimits the
    r.o.i. and the black arrow shows the site of stimulation in GD.
  }\label{lfpevocada}
\end{figure}

\begin{figure}[H]
  \captionsetup{singlelinecheck=off} 
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_completa_evocada3R7.pdf}
\caption[tu abueala]{
  \begin{intension}
    En esta imagen y la siguiente se compara la representación de
    LFP, CSD y CM. La idea es que se pueda apreciar la ventaja
    en limpieza y localización que ofrece CSD, y que se entienda
    como manejar los centros de masa a partir de aquella.
    También muestra como es posible separar la acción de un grupo
    de electrodos inservible porque su Centro de Masa no se mueve.
  \end{intension}

  Comparison of the activity represented as LFP, CSD and CM.
  The time after
  stimulation in ms is shown in the central column for each row.
  In this series of frames a relatively big patch of the electrodes
  still appear saturated, but even so the CSD shows good localization
  of the relevant deflections from the neutral or noise base signal.
  The CM representation concentrates the locus of action even more.
  The circular dots in the third column represent the center of mass
  of coherent active subsets.
}\label{lfpcsdcm}
\end{figure}

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
   \includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_sub_evocada3R7.pdf}
   \caption[tu abuela]{
     \begin{intension}
       Misma intensión general que la figura anterior pero en un
       recuadro específico. La idea es mostrar claramente los componentes
       disjuntos en CA3 y su Centro de Masa a detalle, en la tercera columna.
       Un punto muy claro es ver como los componentes se pueden disolver
       en componentes más pequeños.
     \end{intension}

     The same as previous figure, but focusing on the
  region of interest, including the stratum pyramidale of CA3. A different
  color scheme was chosen on the last column, so as to provide borders
  that show how the disconnected components where chosen. 
}\label{lfpcsdcmsub}
\end{figure}

@@

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
 \includegraphics[width=0.7\textwidth]{./Figuras/trayevocadasub.pdf}
 \caption[tu abuela]{
   \begin{intension}
     Primera muestra de trayectorias. Escogemos sólo la parte
     respondiente del potencial evocado, para claridad. Se debe
     poder apreciar como las trayectorias corren sobre
     los diferentes estratos y sus tiempos de desplazamiento
     son esperados dentro de las escalas de distancia y sincronización.
   \end{intension}
   The evoked trajectories in the r.o.i. We begin to track them
    at the 0.9 ms mark, after letting the saturation of the stimulus recede.
    At 3ms a very clear sink trajectory is moving retrogradly towards CA2,
    shepherd by two shorter source trajectories. At 5.6 a depolarization
    trajectory starts, following almost the same path and presenting also its
    two companions, ending around the 7.7ms timestamp. No significant
  trajectories are observed after the 10ms mark. }\label{evotracks}
\end{figure}

@@

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.7\textwidth]{Figuras/diagfacilitada.pdf}
  \caption[tu abuela]{
  \begin{intension}
    Mostrar un diagrama de los estratos importantes. Se puede incorporar
    a otra figura.
  \end{intension}
  A diagram of the approximate location of the pyramidal and granular strata on the hippocampus slice, during a peak of activity as measured in \muV{}.
  }
  \label{diagfaci}
\end{figure}

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_facilitada.pdf}
\caption[tu abuela]{
  \begin{intension}
    Intensión similar a la figura \ref{lfpcsdcmsub}, pero
    usando el área de registro completa. Se muestra la diversidad
    de escalas que abarcan los posibles componentes, por ejemplo,
    los muy grandes en las lineas centrales, en CA3, y los pequeños en
    la cola de CA1 en los últimos renglones. 
  \end{intension}

  Comparison of the activity represented as LFP, CSD and CM,
  in the same style as fig. \ref{lfpcsdcm}, but for facilitated activity.
  In this case the time counter starts at some moment around 80 ms. before the
  onset of the burst of activity.
}\label{lfpcsdcmfaci}
\end{figure}

\begin{figure}[H]
  \captionsetup{singlelinecheck=off}
  \includegraphics[width=0.7\textwidth]{./Figuras/trayfaciljuntas.pdf}
\caption[tu abuela]{
  \begin{intension}
    Imagen de área de registro completo mostranto las trayectorias.
    Después de la figura \ref{evotracks}, esta figura muestra
    la riqueza estructural en los datos generados con éste análisis,
    y muestra la posibilidad ( intuitivamente ) de agrupar visualmente
    los diferentes manchones de trayectorias a esta escala. 
  \end{intension}
 The trajectories for  the facilitated activity, in
 sequence of apparition around the burst of action.}\label{facitracks}
\end{figure}

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
 \includegraphics[width=0.7\textwidth]{./Figuras/traytodasfacilitada.png}
 \caption[tu abuela]{
   \begin{intension}
     Remate de la figura \ref{facitracks}. En la ampliación es mucho más fácil
     discernir diferentes tipos de trayectorias. En CA3 corren a lo largo
     de los estratos, mientras que en CA1 son primordialmente transversales.
     También se puede apreciar un área de transición con menor densidad. 
   \end{intension}

 The trajectories for  the facilitated activity, shown
 all together.}\label{facitracktodas}
\end{figure}

@@

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.9\textwidth]{./Figuras/LFPvsCSD_4AP.pdf}
  \caption[tu abuela]
  { \begin{intension}
      En esta figura muestro LFP contra CSD con ruido espacial y
      sin ruido espacial. Esta vez estoy probando ordenar por
      columnas en lugar de por renglones, probando otra representación.
      A diferencia de otras figuras, aquí muestro explicitamente
      la ayuda de usar un filtro gaussiano espacial para
      ``limar el ruido''. 
    \end{intension}
    Comparison of LFP and CSD representations
    at the moments of the epileptic burst. In the first row
    we present the data as measured, no denoising or filtering has
    been applied. The units of measurement are in $\muV{}$. In
    the middle row a direct application of a difference operator
    gives us the CSD. This sort of operators are very sensitive
    to noise, in this case, spatial hard edges, which become
    greatly exaggerated. In the third row we present the same
    data after a Gaussian spatial filter ( Gaussian Blur) has
    been applied. }\label{lfpycsd4ap}
\end{figure}

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.9\textwidth]{./Figuras/Fronteras2sigma.pdf}
  \caption[tu abuela]
    {
      \begin{intension}
        Una vez más enfatizamos la importancia del filtro gaussiano.
        En el renglón superior mostramos como los componentes disconexos
        quedan demasiado pequeños, y se pierde significancia en un mar de
        ruido, mientras que en el inferior aparecen subconjuntos coherentes.
      \end{intension}

            The detection of disconnected components for the Sink and Source
    Sets. We take the the threshold value as two times the
    standard deviation of the whole data in CSD representation. In
    the upper row the data without the Gaussian Blur filtering is shown.
    Although the location of some of the active sets is clear, a lot of the
    joint activity gets hidden under the spatial noise. In the lower
    row we repeat the detection with the smoothed data. Large, coherent
    patches of activity are clearly shown, and the structure of the
    stratum pyramidale is apparent. 
  }\label{csdfrontera}
\end{figure}

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.9\textwidth]{./Figuras/SeqTray4AP01.pdf}
  \caption[tu abuela]{
    \begin{intension}
      Partiendo del renglón inferior de la figura \ref{csdfrontera}
      mostramos la aparición y sucesión de trayectorias bien definidas
      sobre str.pyr. y el giro dentado (primer ejemplo donde es claramente
      discernible su aportación a las trayectorias). 
    \end{intension}
    The activity in the Center of Mass and Trajectories representation.
    A single epileptic attack is shown from slightly before the onset until the
    last wave of the attack. Sink and Source trajectories are shown in blue
    and red, respectively. In order to not saturate the latter subfigures
    we take a persistence value of 2 ms, meaning that we do not shown
    trajectories 2 ms after they have ended.}\label{tray4ap}.
 \end{figure}

@@

The stratial tissue is an example of where this analysis cannot be used.
The limitation of this technique is that it works  in
ordered, stratified neuronal tissue, and highly homogeneous tissue
without clear structures makes the distinction of both the CSD and
disconnected sets unfeasible.

\begin{figure}[H]
 \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.7\textwidth]{Figuras/lfpestriado.pdf}
  \caption[tu abuela]{
    \begin{intension}
      Esta figura contrasta mucho con la figura \ref{lfpevocada}.
      Bajo la misma representación, tenemos muy claro que no hay
      estructuras discernibles. Sin embargo, requiere una serie de trazos
      bien escogidos para saber si hay actividad relevante.
    \end{intension}
    LFP stratial Tissue, some samples. There are no discernible
    structures. The apparent active set at the lower left corner
  is an artifact due to some bubbles in the experiment.}
\end{figure}

\begin{figure}[H]
   \captionsetup{singlelinecheck=off} 
  \includegraphics[width=0.7\textwidth]{Figuras/traytodasestriado.pdf}
  \caption[tu abuela]{
    \begin{intension}
      Una muestra clara de que el tejido estriado no
      permite la búsqueda de trayectorias definidas. A pesar
      de contar con un registro mucho más amplio, apenas alcanzamos a
      ver un par de trayectorias ``fuente'' en lo que aparente ser
      un artefacto del ruido y no cuentan con ``pozos'' que acompañen.
    \end{intension}
    After 30 seconds of recording, no visible trajectories can be found. The minimum displacement criteria is not full-filed for most of the putative centers of mass. Only a small set of trajectories is seen on the lower corner and these seem to correspond to an artifact due to a bubble in the recording. }

\end{figure}
